%\documentclass[12pt,draftcls,onecolumn]{IEEEtran}
%\documentclass[12pt,twocolumn]{IEEEtran}
\documentclass[twocolumn]{IEEEtran}
\usepackage{times}

% Packages, commands --------------------------------------------------------------------
\input{pack}

% BIBLIOGRAHY -----------------------------------------------------------------------------
% Option 1: bibtex natbib
%\usepackage[numbers]{natbib}
%\usepackage[colorlinks=true,linkcolor=blue,citecolor=purple,pagebackref=true]{hyperref}
% Option 2: biblatex 
%\usepackage[backend=bibtex,style=ieee-alphabetic,natbib=true,backref=false]{biblatex}
\usepackage[backend=bibtex,style=ieee,natbib=true,backref=false]{biblatex}
\addbibresource{ref.bib}
% Adding back references to bib entries:
\DefineBibliographyStrings{english}{%
  backrefpage = {page},% originally "cited on page"
  backrefpages = {pages},% originally "cited on pages"
}
% Title, authors, etc. -------------------------------------------------------------------------

%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
\title{A Linearly Relaxed Approximate Linear Program for Markov Decision Processes}
%\author{Chandrashekar Lakshminarayanan$^\star$, Shalabh Bhatnagar$^\star$,
 and Csaba Szepesvari$^\dagger$\thanks{$^\star$Department of Computer
Science and Automation, Indian Institute of Science, Bangalore 560012.
E-mail: $\{$chandrul, shalabh$\}$@csa.iisc.ernet.in}
\thanks{$^\dagger$Department of Computing Science, University of Alberta,
Edmonton, Alberta, Canada T6G 2E8. E-mail: csaba.szepesvari@ualberta.ca}}
% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.
\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

% Doc start ------------------------------------------------------------------------------------
\begin{document}
%\maketitle
Dear Editor,
            We would like to re-submit the revised version of our paper. We now list the differences between the previous and current submission.
\begin{itemize}
\item The title of the paper has been changed to ``A Linearly Relaxed Approximate Linear Program for Markov Decisions Processes''.
\item The length of current draft has been increased to 8 pages.
\item We have incorporated major revisions in the paper and restructure the presentation.
\item The length of the introduction has been increased to make the motivation clear. Proper placement with respect to existing literature has been done.
\item The main result has been stated up front alongside a discussion.
\item Streamlined formulation of the main result, with additional corollary that illustrates the utility. Added examples.
\item The proof has been simplified and restructured. The constants in the bound have been slightly improved.
\item Numerical illustration: New example has been added to illustrate the choices available when choosing constraints.
\end{itemize}
We have taken care of all the reviewer comments, except for the following comment by Reviewer~$1$.
\emph{Comment}: Explain the intuition behind stationary Markov deterministic policies being optimal.
\emph{Our Response:} Markov property buys this. Since we are limited by space constraints we have added reference to literature.
\end{itemize}
\end{document}
